A Formal Model of Checked C

### 2023-01-18 sandp23/evaluation.tex
Fixing eval

\subsection{Dataset}
\input{tables/datasettable}
Network-facing programs such as servers directly interact with external input, often process complex data types, and are more susceptible to security issues.
We primarily focus on network servers as they can benefit most from our partitioning approach.
We use WebAssembly (WASM) as our target sandbox. Consequently, we also want any of the selected programs to be compilable with the WASM sandbox.
We selected network servers that we could (with minimal effort) compile with the WASM compiler.
We also selected a few standalone programs suggested by the ~\checkedc team~\cite{benchmarkcc}, which are good candidates to evaluate modifications to~\checkedc.
The~\tbl{table:dataset} shows the program selected as part of our evaluation dataset. 
In our conversion, we re-introduce corrected memory bugs and then perform \systemname annotations on the relevant buggy code.
However, this is based on the assumption that the bugs are predicted before they are discovered, which is chronologically impossible.
Consequently, we also annotate large sections of relevant bug-free code to mimic the developer's intuition on making \systemname annotations 
without input on the bug locality.

@@

As in~\fig{fig:microbenchmarks}, we incur 34\% overhead in accessing tainted pointers in~\cregion,
 due to additional validation checks, which require executing two compare instructions for every memory access.

@@

\input{figures/memoryoverhead}

ProFTPD's run-time overhead is expected as our conversion was small and strictly encapsulates CVE-2010-4221.
Since UFTPD's test-suite lacks coverage for some of the \systemname changes, we manually write a script for 3 Tests that each trigger "quote CWD", "quote PORT", and FTP "get file" on a 4.0K file, following which, we record overhead as described in ~\ref{experimentalsetup}.
Run-time overhead for UFTPD is expected as the sandboxed code was less performance intensive and FTP-protocol by itself overshadows \systemname's overhead.

Our evaluation of \systemname's performance results on the dataset yields the observations:
\begin{itemize}
  \item Run-time Overhead is proportional to the extent of 
annotated pointers and sandboxed code.
  \item Marshalling can be avoided if Taintedness of a pointer is propagated across its data-flow.
  \item Marshalling might sometimes be relatively cost-effective instead of propagating the taintedness of a pointer throughout its data-flow. 
\end{itemize}

\subsection{Security Impact}
\label{subsec:securityimpact}
The last column of the Table ~\ref{table:conversioneffort} shows the list of all spatial safety vulnerabilities in the functions that have tainted types or are isolated in the~\ucregion{}.
As expected,~\emph{all vulnerabilities} are prevented by~\systemname{}.

>>>>

\subsection{Dataset}
\input{tables/datasettable}
Network-facing programs such as servers directly interact with external input, often process complex data types, and are more susceptible to security issues.
We primarily focus on network servers as they can benefit most from our partitioning approach.
We use WebAssembly (WASM) as our target sandbox. Consequently, we also want any of the selected programs to be compilable with the WASM sandbox.
We selected network servers that we could (with minimal effort) compile with the WASM compiler.
We also selected a few standalone programs suggested by the ~\checkedc team~\cite{benchmarkcc}, which are good candidates to evaluate modifications to~\checkedc.
The~\tbl{table:dataset} shows the program selected as part of our evaluation dataset.

@@

As shown in~\fig{fig:microbenchmarks}, we incur 34\% overhead in accessing tainted pointers in~\cregion,
 due to additional validation checks, which require executing two compare instructions for every memory access.

@@

\input{figures/memoryoverhead}
The~\fig{fig:runtimeoverhead} shows the overhead of the partitioned programs.
It is interesting to see a lot of variance in the runtime overhead.
Our analysis shows that the runtime overhead is proportional to the execution time spent in the sandbox and the number of transitions between~\cregion and the sandbox.
This is expected because of the overhead in sandbox execution, as shown by our micro-benchmarks experiments (\fig{fig:microbenchmarks}).
The~\tbl{table:conversioneffort} shows the number of lines in the sandbox for each of the partitioned programs.
For~\texttt{ProFTPD}, we used only tainted pointers with no code in the sandbox, and there were also no transitions to/from the sandbox.
Consequently, the overhead is very less 4.2\%.
For~\texttt{UFTPD} and~\texttt{MicroHTTPD}, we partitioned only request handlers (that are relatively small) into the sandbox. These handlers parse the message and return the actions that need to be performed. The server only invokes these handles on particular requests resulting in less number of transitions into the sandbox. As expected, the overhead is also very less in these cases.
For~\texttt{TinyBigNum} and~\texttt{Parsons}, the overhead is very high because of the relatively large amount of code in sandbox region.
In both these applications, we place the frequently used parsing functions in the sandbox resulting in a lot of sandbox transitions with most of them in a loop.
As expected, the overhead is very high.
The case is slightly different in~\texttt{pnm2png} and~\texttt{png2pnm} where we made the entire~\code{png} structure tainted, which resulted in dynamic checks every time any part of the~\code{png} struct is accessed, resulting in slightly higher overhead.
In summary:
\begin{itemize}
  \item The runtime overhead of the partioned program directly depends on that of the target sandbox.
  \item Run-time Overhead is proportional to the extent of annotated pointers, sandboxed code, and transitions between~\cregion and sandbox.
  \item Tainting heavily used pointers leads to high overhead.
\end{itemize}

%ProFTPD's run-time overhead is expected as our conversion was small and strictly encapsulates CVE-2010-4221.
%Since UFTPD's test-suite lacks coverage for some of the \systemname changes, we manually write a script for 3 Tests that each trigger "quote CWD", "quote PORT", and FTP "get file" on a 4.0K file, following which, we record overhead as described in ~\ref{experimentalsetup}.
%Run-time overhead for UFTPD is expected as the sandboxed code was less performance intensive and FTP-protocol by itself overshadows \systemname's overhead.

%Our evaluation of \systemname's performance results on the dataset yields the observations:
%\begin{itemize}
%  \item Run-time Overhead is proportional to the extent of 
%annotated pointers and sandboxed code.
%  \item Marshalling can be avoided if Taintedness of a pointer is propagated across its data-flow.
%  \item Marshalling might sometimes be relatively cost-effective instead of propagating the taintedness of a pointer throughout its data-flow. 
%\end{itemize}

\subsection{Security Impact}
\label{subsec:securityimpact}
The last column of the Table ~\ref{table:conversioneffort} shows the list of all spatial safety vulnerabilities in the functions that have tainted types or are isolated in the~\ucregion{}.
We re-introduced these bugs in the annotated program and checked whether these bugs could be triggered by the corresponding crashing input or exploit (if available).
We also manually verified whether the bug can be triggered or prevented by~\systemname{}.
As expected,~\emph{all vulnerabilities} are prevented by~\systemname{}.

### 2023-01-18 sandp23/tables/datasettable.tex
Fixing eval

{
\footnotesize
\begin{table}[]
\begin{tabular}{c|c|c|r}
\toprule
\textbf{ID} & \textbf{Program} & \textbf{Description}          & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Size\\ (SLoc)\end{tabular}}} \\ 
\midrule
\rowcolor{black!15} 1           & ProFTPD          & High performance FTP Server   & 556 K                                                                               \\ 
2           & MicroHTTPD       & Simple HTTPD Server           & 122 K                                                                                \\ 
\rowcolor{black!15} 3           & UFTPD            & UDP based FTP Server          & 3 K                                                                               \\ 
4           & LibPNG          & Program to convert between png and pnm & 76 K                                                                               \\ 
\rowcolor{black!15}5           & TinyBigNum          & Multiple-precision integer implementation & 1.6 K                                                                               \\ 
6           & Parsons          & JSON parsing library & 3.1 K                                                                               \\

>>>>

{
\scriptsize
\begin{table}[]
\begin{tabular}{c|c|c|r}
\toprule
\textbf{ID} & \textbf{Program} & \textbf{Description}          & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Size\\ (SLoc)\end{tabular}}} \\ 
\midrule
\rowcolor{black!15} 1           & ProFTPD          & High performance FTP Server   & 556 K                                                                               \\ 
2           & MicroHTTPD       & Simple HTTPD Server           & 122 K                                                                                \\ 
\rowcolor{black!15} 3           & UFTPD            & UDP based FTP Server          & 3 K                                                                               \\ 
4           & \multicolumn{1}{c|}{\begin{tabular}[c]{@{}c@{}}LibPNG\\ (png2pnm and pnm2png)\end{tabular}}           & Program to convert between png and pnm & 76 K                                                                               \\ 
\rowcolor{black!15}5           & TinyBigNum          & Multiple-precision integer implementation & 1.6 K                                                                               \\ 
6           & Parsons          & JSON parsing library & 3.1 K                                                                               \\
